Association between trauma severity models and opportunities for improvement:

### 2022-09-23 manuscript.Rmd
a working flowchart for inclusion/exclusion numbers

---
title: "Association between trauma severity models and opportunities for improvement: A retrospective cohort study"
author: "Victoria Witthoff"
output:
  pdf_document: default
  html_document: default
bibliography: bibliography.bib
csl: vancouver.csl
---

@@

@@

```{r main, echo=FALSE, message = FALSE}
  source("main.R") ## This "imports" the main script file of your project and run any code in it
  as.data.frame(t1)
```

>>>>

---
title: 'Association between trauma severity models and opportunities for improvement:
  A retrospective cohort study'
author: "Victoria Witthoff"
output:
  html_document: default
  pdf_document: default
  word_document: default
bibliography: bibliography.bib
csl: vancouver.csl
---

@@

```{r main, echo=FALSE, message = FALSE}
  source("main.R") 
  exclusion_flowchart(inclusion.counts)
```

@@
